---
title: "Project 4"
output: html_notebook
---

packages
```{r}


#source
```


# Step 1: Load Data
```{r}

```

## Reshape Data
```{r}

# Save wide ms data to Rdata


# Save wide movie data to Rdata
```

# Step 2: Compute Similarity (weight)
## Vector Similarity
### MS data
```{r}


# Save weight in output
```

### Movie data
```{r}


# Save weight in output
```

## Mean Sqaure Difference
### MS data
```{r}


# Save weight in output
```

### Movie data
```{r}


# Save weight in output
```

## Simrank (movie)
Note: simrank method is written in python
```{r}
# read in the simrank weight

# Sace weight in output
```

# Step 3: Cross validate parameters for different selecting neighbor methods
## Weight Threshold
```{r}

```

## Best-n-estimators
```{r}

```

## Combine
```{r}

```

# Step 4: Prediction & Evaluation
## MAE
### MS Data
```{r}

```

## Movie Data
```{r}

```

## Rank Score
### MS Data
```{r}

```

### Movie Data
```{r}

```

# Step 5: Model-based Algorithm
## Clustering (MS Dataset)
```{r}

```

# Step 6: Prediction & Evaluation
## MAE
```{r}

```

## Rank Score
```{r}

```

