---
title: "Project 4"
output:
  pdf_document: default
  html_notebook: default
---
# Overview
In this project, we aim to predict user-item score through collaborative filtering. In the memoery based methods, we adopted 3 similarity metrics (vector similarity, mean square difference and simrank) to calculate weight, in step 2.And then, we used weight threshold and best-n-estimator, or a combination of both to select neighbours. As for evaluation, we implemented mae and ranked scoring. In order to find the suitable threshold and the best n, we tuned those parameters in step 3.  
\newline
In step 5 and 6, we implemented and evaluated the performance of a model based method: clustering. 

load packages
```{r}
library(reshape2)
library(ggplot2)
```


# Step 1: Load Data
```{r}
movie_train_raw <- read.csv('../data/data_sample/eachmovie_sample/data_train.csv',header = T)
movie_test_raw <- read.csv('../data/data_sample/eachmovie_sample/data_test.csv',header = T)
MS_train_raw <- read.csv('../data/data_sample/MS_sample/data_train.csv',header = T)
MS_test_raw <- read.csv('../data/data_sample/MS_sample/data_test.csv',header = T)
```

## Reshape Data
```{r}
# ms data
source('../lib/preprocess.R')
## load processed data
load('../output/ms_train.RData')
load('../output/ms_test.RData')

# movie data
## train
dcast_train <- dcast(movie_train_raw, User~Movie)
rownames(dcast_train) <- dcast_train$User
movie_train <- dcast_train[,-1]
## test
dcast_test <- dcast(movie_test_raw, User~Movie)
rownames(dcast_test) <- dcast_test$User
movie_test <- dcast_test[,-1]
## save file
savefile = FALSE
if(savefile == TRUE) save(movie_train,movie_test, file = '../output/movie_wide.RData')
load('../output/movie_wide.RData')
```

# Step 2: Compute Similarity (weight)
## Vector Similarity
### Movie data
```{r}
# load vector similarity function
source('../lib/mat_weight.R')

# whether run vector similarity and whether save csv file
run.vec = FALSE
save.rd = FALSE
movie_vec_weight <- mat_weight(data = movie_train_raw, 
                              run.vec = run.vec,
                              run.msd = FALSE)

# save output in RData
if(save.rd == TRUE) save(movie_vec_weight, file = '../output/movie_vec_weight.RData')

# load output data
load('../output/movie_vec_weight.RData')
```

### MS data
```{r}
# whether run vector similarity and whether save csv file
run.vec = FALSE
save.rd = FALSE
ms_vec_weight <- mat_weight(data = ms_train, 
                           run.vec = run.vec,
                           run.msd = FALSE)

# save output in RData
if(save.rd == TRUE) save(ms_vec_weight, file = '../output/ms_vec_weight.RData')

# load output data
load('../output/ms_vec_weight.RData')
```

## Mean Sqaure Difference
### Movie data
```{r}
# whether run vector similarity and whether save csv file
run.msd = FALSE
save.rd = FALSE
movie_msd_dissimilar <- mat_weight(data = movie_train_raw, 
                                   run.vec = FALSE,
                                   run.msd = run.msd)
# convert dissimilarity to similarity weight
movie_msd_weight <- (max(movie_msd_dissimilar) - movie_msd_dissimilar ) /
  ( max(movie_msd_dissimilar) - min(movie_msd_dissimilar) )

# save output in RData
if(save.rd == TRUE) save(movie_msd_weight, file = '../output/movie_msd_weight.RData')

# load output data
load('../output/movie_msd_weight.RData')

```

### MS data
```{r}
run.msd = FALSE
save.rd = FALSE
ms_msd_dissimilar <- mat_weight(data = ms_train, 
                            run.vec = FALSE,
                            run.msd = run.msd)

# convert dissimilarity to similarity weight
ms_msd_weight <- (max(ms_msd_dissimilar) - ms_msd_dissimilar ) /
  ( max(ms_msd_dissimilar) - min(ms_msd_dissimilar) )

# save output in RData
if(save.rd == TRUE) save(ms_msd_weight, file = '../output/ms_msd_weight.RData')

# load output data
load('../output/ms_msd_weight.RData')
```

## Simrank (movie)
Note: simrank method is written in python
```{r}
# read in the simrank weight
load('../output/movie_simrank_weight.RData')
```

# Step 3: Tune parameters for different selecting neighbor methods

load functions
```{r}
source('../lib/tuning.R')
```

## Weight Threshold
```{r}
threshold <- seq(0.1,0.5,by = 0.1)
```

## Best-n-estimators
```{r}
bestn <- seq(5, 200, by = 5)
```

## Combine
```{r}
threshold <- seq(0.3,0.5,by = 0.1)
bestn <- seq(16, 30, by = 2)
par = list(threshold,bestn)
```

## final parameter
```{r}
best.par <- list(n = 60, threshold = 0.6)
```
# Step 4: Prediction & Evaluation

## load functions
```{r}
source('../lib/predict_score.R')
```

### MS test Prediction
```{r}
# chose which selecting neighbor method to use
run.bestn = TRUE
run.threshold = TRUE
# using vector similarity weight
pred.ms.vec <- predict.score.ms(ms_train,
                                ms_test,
                                ms_vec_weight,
                                par = best.par,
                                run.threshold = run.threshold,
                                run.bestn = run.bestn)
# using msd weight
pred.ms.msd <- predict.score.ms(ms_train,
                                ms_test,
                                ms_msd_weight,
                                par = best.par,
                                run.threshold = run.threshold,
                                run.bestn = run.bestn)
```

## Movie Data
```{r}
# chose which selecting neighbor method to use
run.bestn = TRUE
run.threshold = TRUE
# using vector similarity weight
pred.movie.vec <- predict.score.movie(movie_train,
                                      movie_test,
                                      movie_vec_weight,
                                      par = best.par,
                                      run.threshold = run.threshold,
                                      run.bestn = run.bestn)
# using msd similarity weight
pred.movie.msd <- predict.score.movie(movie_train,
                                      movie_test,
                                      movie_msd_weight,
                                      par = best.par,
                                      run.threshold = run.threshold,
                                      run.bestn = run.bestn)
# using simrank weight
pred.movie.simrank <- predict.score.movie(movie_train,
                                          movie_test,
                                          movie_simrank_weight,
                                          par = best.par,
                                          run.threshold = run.threshold,
                                          run.bestn = run.bestn)
```

## MAE
load functions
```{r}
load('../lib/mea.R')
```
### MAE for MS Data
```{r}
mae.ms.vec <- MAE(pred.ms.vec, ms_test)
mae.ms.vec
```
### MAE for Movie Data
```{r}
mae.movie.vec <- MAE(pred.movie.vec, movie_test)
mae.movie.vec
```

## Rank Score
load functions
```{r}
load('../lib/ranked_scoring.R')
```
### Rank score MS Data
```{r}
rankscore.ms.vec <- rank_matrix(pred.ms.vec, ms_test)
rankscore.ms.vec
```
### Rank score Movie Data
```{r}
rankscore.movie.vec <- rank_matrix(pred.movie.vec, movie_test)
rankscore.movie.vec
```

# Step 5: Model-based Algorithm
## Clustering (MS Dataset)
### Cross Validating the cluster model to find best cluster number C
```{r}
source("../lib/cluster_model.R")

preprocess_for_cluster(preprocess.train = F, preprocess.test = F, reshape.train = F, reshape.test = F)

load("../output/ms_train_wide.RData")
load("../output/ms_test_wide.RData")

list_of_items <- names(train[,-1])

cross.validate.model.clustering <- FALSE
if(cross.validate.model.clustering){
  r <- c()
  parameters <- c(4,5,6,7,8)
  for(par in parameters){
    trained.cluster.model <- train.cluster.model(train, C = par)
    g <- trained.cluster.model$gamma_array
    m <- trained.cluster.model$mu
    p <- trained.cluster.model$pi_mat
    testing <- test.cluster.model(test, gamma_array = g, mu = m, pi_mat = p, list_of_items = list_of_items)
    r <- c(r, testing$r)
    print(paste("For number of clusters equal to:", par, "Rank score:", testing$r))
  }
  
  t <- matrix(NA, ncol = length(parameters), nrow = 2)
  t[1,] <- parameters
  t[2,] <- r
  rownames(t) <- c("C", "Rank Score")
  save(t, file = "../output/cv_cluster_rank_score.Rdata")
}

```

# Step 6: Evaluation for Cluster model
## Rank Score
load output rank score
```{r}
load("../output/cv_cluster_rank_score.Rdata")
```
print output
```{r}
print(t)
best.C <- as.numeric(t[1, which.max(t[2,])])
best.rank.score <- as.numeric(max(t[2,]))
print(paste("The best cluster number is:", best.C, ". Rank score is:", best.rank.score))
```

